### 2022-08-05 README.Rmd
Added sim_ame(), other changes and fixes; ready for testing

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

@@

You can install the development version of simbased from [GitHub](https://github.com/) with:

@@

```{r example}
library(simbased)

@@

sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(RR = p1 / p0)
}, verbose = FALSE)

summary(sim_est)
sim_plot(sim_est)
```

@@

```{r}
marginaleffects::comparisons(fit, variables = list(treat = 0:1),
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary(transform_avg = exp)
```

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```

@@

You can install the development version of `simbased` from [GitHub](https://github.com/) with:

@@

```{r example, fig.width=7, fig.height=3}
library(simbased)

@@

sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, RR = p1 / p0)
}, verbose = FALSE)

summary(sim_est, null = c(NA, NA, 1))
sim_plot(sim_est)
```

@@

```{r}
# Marginal risk ratio ATT, delta method-based
marginaleffects::comparisons(fit, variables = list(treat = 0:1),
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary(transform_avg = exp)
```

@@

`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the marginal risk ratio below:

```{r}
# Marginal risk ratio ATT, simulation-based
sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
                   contrast = "RR", verbose = FALSE)

summary(sim_est, null = c(NA, NA, 1))
```

We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

```{r, fig.width=7, fig.height=3}
# Predictions across age and treat at typical values
# of the other predictors
sim_est <- sim_setx(sim_coefs, x = list(age = 20:50, treat = 0:1),
                    verbose = FALSE)

setx_plot(sim_est)
```

`simbased` offers parallel processing for all estimation functions to speed up computation.

The methodology of simulation-based inference is described in King, Tomz, and Wittenberg (2000).

King, G., Tomz, M., & Wittenberg, J. (2000). Making the Most of Statistical Analyses: Improving Interpretation and Presentation. *American Journal of Political Science*, 44(2), 347–361. https://doi.org/10.2307/2669316
